Data_visualization

### 2018-08-03 Rmd/ggplot_2_species_trial.Rmd
last changes

---
title: "Data_visualization"
output:
      pdf_document
---
```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=6, fig.width=7,out.width='100%'}
#Preparing seed set plots, starting with Petunia

@@

grobz <- lapply(list(a, b, c, d), ggplotGrob)
grobz.plot <- arrangeGrob( grobs = list(rbind(grobz[[1]], grobz[[3]], size = "last"),
                                        rbind(grobz[[2]], grobz[[4]], size = "last")),
                           ncol = 2, top="Solanaceae Focal Species")

@@

```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=6, fig.width=7,out.width='100%'}
library(dplyr)

#load libraries
library(reshape2)
library(ggplot2)
library(dplyr)
library(gridExtra)
library(grid)
library(lattice)
library(gtable)
##
###
#B. OLERACEA
###
##
#

brol_seed_set <- read.csv("Data/BROL_seed_set.csv", sep=";")
brol_seed_set <- filter(brol_seed_set, Treatment!="RARA 100%" & Treatment!="RARA 50%"& Treatment!="COSA 50%"& Treatment!="COSA 100%" )

#adding the focal species, first 50%
Species <- rep("BROL", 10)
Treatment <- rep("BROL 50%", 10)
Treatment.number <- seq(1:10)
Seed.production <- rep(0, 10)
brol_50 <- data.frame(Species,Treatment, Treatment.number, Seed.production)
#adding the focal species, 100%
Species <- rep("BROL", 10)
Treatment <- rep("BROL 100%", 10)
Treatment.number <- seq(1:10)
Seed.production <- rep(0, 10)
brol_100<-  data.frame(Species,Treatment, Treatment.number, Seed.production)
#Order from lower to higher values the average, to plot it nicely
colnames(brol_seed_set)[1] <- "Species"
colnames(brol_seed_set)[2] <- "Treatment"
colnames(brol_seed_set)[3] <- "Treatment.number"
colnames(brol_seed_set)[4] <- "Seed.production"
brol_seed_set <- rbind(brol_seed_set, brol_50, brol_100)
brol_seed_set$Treatment<- as.character(brol_seed_set$Treatment)
brol_seed_set <- brol_seed_set[order(brol_seed_set$Treatment),]

library(stringr)
brol_seed_set_div <- str_split_fixed(as.character(brol_seed_set$Treatment), " ", 2)
brol_seed_set_div <- data.frame(brol_seed_set_div, stringsAsFactors = F)
colnames(brol_seed_set_div)=c("non_focal","percentage")
brol_seed_set_bind <- cbind(brol_seed_set,brol_seed_set_div)
brol_seed_set_bind <- filter(brol_seed_set_bind, percentage!="100%")

#Because I want to give it specifically order I do it separately
#pein_seed_set_common <- filter(brol_seed_set_bind, non_focal %in% c("CROSS", "SELF","CONTROL","FLOWER"))

brol_seed_set_cross <- filter(brol_seed_set_bind, non_focal %in% c("Cross"))
brol_seed_set_self <- filter(brol_seed_set_bind, non_focal %in% c("Self"))
brol_seed_set_control <- filter(brol_seed_set_bind, non_focal %in% c("Control"))
brol_seed_set_flower <- filter(brol_seed_set_bind, non_focal %in% c("FC"))

# I HAVENT BEEN ABLE TO WORK OUT ALL AT THE SAME TIME SO i DO IOT SEPARATELY
brol_seed_set_bind=brol_seed_set_bind[brol_seed_set_bind$non_focal!=c("Cross"),]
brol_seed_set_bind=brol_seed_set_bind[brol_seed_set_bind$non_focal!=c("Self"),]
brol_seed_set_bind=brol_seed_set_bind[brol_seed_set_bind$non_focal!=c("Control"),]
brol_seed_set_bind=brol_seed_set_bind[brol_seed_set_bind$non_focal!=c("FC"),]

brol_seed_set_final<-rbind(brol_seed_set_bind,brol_seed_set_cross, brol_seed_set_self, brol_seed_set_control,
                           brol_seed_set_flower)
#deleting extra columns used for data formating
brol_seed_set_final=brol_seed_set_final[,-c(5,6)]
#adding NA'S to the focal species
brol_seed_set_final[brol_seed_set_final$Treatment==c("BROL 50%"),4] <- NA

#changing non_focal species name
brol_seed_set_final$Treatment=as.character(brol_seed_set_final$Treatment)
brol_seed_set_final$Family[brol_seed_set_final$Treatment=="BROL 50%"] <- "Brassicaceae"
brol_seed_set_final$Family[brol_seed_set_final$Treatment=="BRRA 50%"] <- "Brassicaceae"
brol_seed_set_final$Family[brol_seed_set_final$Treatment=="SIAL 50%"] <- "Brassicaceae"
brol_seed_set_final$Family[brol_seed_set_final$Treatment=="ERSA 50%"] <- "Brassicaceae"
brol_seed_set_final$Family[brol_seed_set_final$Treatment=="CAAN 50%"] <- "Solanaceae"
brol_seed_set_final$Family[brol_seed_set_final$Treatment=="SOLY 50%"] <- "Solanaceae"
brol_seed_set_final$Family[brol_seed_set_final$Treatment=="SOME 50%"] <- "Solanaceae"
brol_seed_set_final$Family[brol_seed_set_final$Treatment=="PEIN 50%"] <- "Solanaceae"
brol_seed_set_final$Family[brol_seed_set_final$Treatment=="IPPU 50%"] <- "Convolvulaceae"
brol_seed_set_final$Family[brol_seed_set_final$Treatment=="IPAQ 50%"] <- "Convolvulaceae"

brol_seed_set_final$Treatment[brol_seed_set_final$Treatment=="BROL 50%"] <- "Brassica oleracea"
brol_seed_set_final$Treatment[brol_seed_set_final$Treatment=="BRRA 50%"] <- "Brassica rapa"
brol_seed_set_final$Treatment[brol_seed_set_final$Treatment=="CAAN 50%"] <- "Capsicum annuum"
brol_seed_set_final$Treatment[brol_seed_set_final$Treatment=="ERSA 50%"] <- "Eruca vesicaria" #Eruca sativa seems to be a synonym
brol_seed_set_final$Treatment[brol_seed_set_final$Treatment=="IPAQ 50%"] <- "Ipomoea aquatica"
brol_seed_set_final$Treatment[brol_seed_set_final$Treatment=="IPPU 50%"] <- "Ipomoea purpurea"
brol_seed_set_final$Treatment[brol_seed_set_final$Treatment=="PEIN 50%"] <- "Petunia integrifolia"
brol_seed_set_final$Treatment[brol_seed_set_final$Treatment=="SIAL 50%"] <- "Sinapis alba"
brol_seed_set_final$Treatment[brol_seed_set_final$Treatment=="SOLY 50%"] <- "Solanum lycopersicum"
brol_seed_set_final$Treatment[brol_seed_set_final$Treatment=="SOME 50%"] <- "Solanum melongena"

#Different colour per family
a <- ggplot(brol_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot()+
  labs(title="Brassica oleracea",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_blank())+
  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.2) + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")

#
##
###
#B. RAPA
###
##
#

brra_seed_set <- read.csv("Data/BRRA_seed_set.csv", sep=";")
brra_seed_set <- filter(brra_seed_set, Treatment!="RARA 100%" & Treatment!="RARA 50%"& Treatment!="COSA 50%"& Treatment!="COSA 100%" )

#adding the focal species, first 50%
Species <- rep("BRRA", 10)
Treatment <- rep("BRRA 50%", 10)
Treatment.number <- seq(1:10)
Seed.production <- rep(0, 10)
brra_50 <- data.frame(Species,Treatment, Treatment.number, Seed.production)
#adding the focal species, 100%
Species <- rep("BRRA", 10)
Treatment <- rep("BRRA 100%", 10)
Treatment.number <- seq(1:10)
Seed.production <- rep(0, 10)
brra_100<-  data.frame(Species,Treatment, Treatment.number, Seed.production)
#Order from lower to higher values the average, to plot it nicely
colnames(brra_seed_set)[1] <- "Species"
colnames(brra_seed_set)[2] <- "Treatment"
colnames(brra_seed_set)[3] <- "Treatment.number"
colnames(brra_seed_set)[4] <- "Seed.production"
brra_seed_set <- rbind(brra_seed_set, brra_50, brra_100)
brra_seed_set$Treatment<- as.character(brra_seed_set$Treatment)
brra_seed_set <- brra_seed_set[order(brra_seed_set$Treatment),]

library(stringr)
brra_seed_set_div <- str_split_fixed(as.character(brra_seed_set$Treatment), " ", 2)
brra_seed_set_div <- data.frame(brra_seed_set_div, stringsAsFactors = F)
colnames(brra_seed_set_div)=c("non_focal","percentage")
brra_seed_set_bind <- cbind(brra_seed_set,brra_seed_set_div)
brra_seed_set_bind <- filter(brra_seed_set_bind, percentage!="100%")

#Because I want to give it specifically order I do it separately
#pein_seed_set_common <- filter(brra_seed_set_bind, non_focal %in% c("CROSS", "SELF","CONTROL","FLOWER"))

brra_seed_set_cross <- filter(brra_seed_set_bind, non_focal %in% c("Cross"))
brra_seed_set_self <- filter(brra_seed_set_bind, non_focal %in% c("Self"))
brra_seed_set_control <- filter(brra_seed_set_bind, non_focal %in% c("Control"))
brra_seed_set_flower <- filter(brra_seed_set_bind, non_focal %in% c("Flower"))

# I HAVENT BEEN ABLE TO WORK OUT ALL AT THE SAME TIME SO i DO IOT SEPARATELY
brra_seed_set_bind=brra_seed_set_bind[brra_seed_set_bind$non_focal!=c("Cross"),]
brra_seed_set_bind=brra_seed_set_bind[brra_seed_set_bind$non_focal!=c("Self"),]
brra_seed_set_bind=brra_seed_set_bind[brra_seed_set_bind$non_focal!=c("Control"),]
brra_seed_set_bind=brra_seed_set_bind[brra_seed_set_bind$non_focal!=c("Flower"),]

brra_seed_set_final<-rbind(brra_seed_set_bind,brra_seed_set_cross, brra_seed_set_self, brra_seed_set_control,
                           brra_seed_set_flower)
#deleting extra columns used for data formating
brra_seed_set_final=brra_seed_set_final[,-c(5,6)]
#adding NA'S to the focal species
brra_seed_set_final[brra_seed_set_final$Treatment==c("BRRA 50%"),4] <- NA

#changing non_focal species name
brra_seed_set_final$Treatment=as.character(brra_seed_set_final$Treatment)
brra_seed_set_final$Family[brra_seed_set_final$Treatment=="BROL 50%"] <- "Brassicaceae"
brra_seed_set_final$Family[brra_seed_set_final$Treatment=="BRRA 50%"] <- "Brassicaceae"
brra_seed_set_final$Family[brra_seed_set_final$Treatment=="SIAL 50%"] <- "Brassicaceae"
brra_seed_set_final$Family[brra_seed_set_final$Treatment=="ERSA 50%"] <- "Brassicaceae"
brra_seed_set_final$Family[brra_seed_set_final$Treatment=="CAAN 50%"] <- "Solanaceae"
brra_seed_set_final$Family[brra_seed_set_final$Treatment=="SOLY 50%"] <- "Solanaceae"
brra_seed_set_final$Family[brra_seed_set_final$Treatment=="SOME 50%"] <- "Solanaceae"
brra_seed_set_final$Family[brra_seed_set_final$Treatment=="PEIN 50%"] <- "Solanaceae"
brra_seed_set_final$Family[brra_seed_set_final$Treatment=="IPPU 50%"] <- "Convolvulaceae"
brra_seed_set_final$Family[brra_seed_set_final$Treatment=="IPAQ 50%"] <- "Convolvulaceae"

brra_seed_set_final$Treatment[brra_seed_set_final$Treatment=="BROL 50%"] <- "Brassica oleracea"
brra_seed_set_final$Treatment[brra_seed_set_final$Treatment=="BRRA 50%"] <- "Brassica rapa"
brra_seed_set_final$Treatment[brra_seed_set_final$Treatment=="CAAN 50%"] <- "Capsicum annuum"
brra_seed_set_final$Treatment[brra_seed_set_final$Treatment=="ERSA 50%"] <- "Eruca vesicaria" #Eruca sativa seems to be a synonym
brra_seed_set_final$Treatment[brra_seed_set_final$Treatment=="IPAQ 50%"] <- "Ipomoea aquatica"
brra_seed_set_final$Treatment[brra_seed_set_final$Treatment=="IPPU 50%"] <- "Ipomoea purpurea"
brra_seed_set_final$Treatment[brra_seed_set_final$Treatment=="PEIN 50%"] <- "Petunia integrifolia"
brra_seed_set_final$Treatment[brra_seed_set_final$Treatment=="SIAL 50%"] <- "Sinapis alba"
brra_seed_set_final$Treatment[brra_seed_set_final$Treatment=="SOLY 50%"] <- "Solanum lycopersicum"
brra_seed_set_final$Treatment[brra_seed_set_final$Treatment=="SOME 50%"] <- "Solanum melongena"

#Different colour per family
b <- ggplot(brra_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot()+
  labs(title="Brassica rapa",x="", y = "")+aes(fill=Family)+theme(axis.text.x = element_blank())+
  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.2) + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")

#
##
###
#E. VERSICARIA
###
##
#

ersa_seed_set <- read.csv("Data/ersa_seed_set.csv", sep=";")
ersa_seed_set <- filter(ersa_seed_set, Treatment!="RARA 100%" & Treatment!="RARA 50%"& Treatment!="COSA 50%"& Treatment!="COSA 100%" )

#adding the focal species, first 50%
Species <- rep("ERSA", 10)
Treatment <- rep("ERSA 50%", 10)
Treatment.number <- seq(1:10)
Seed.production <- rep(0, 10)
ersa_50 <- data.frame(Species,Treatment, Treatment.number, Seed.production)
#adding the focal species, 100%
Species <- rep("ERSA", 10)
Treatment <- rep("ERSA 100%", 10)
Treatment.number <- seq(1:10)
Seed.production <- rep(0, 10)
ersa_100<-  data.frame(Species,Treatment, Treatment.number, Seed.production)
#Order from lower to higher values the average, to plot it nicely
colnames(ersa_seed_set)[1] <- "Species"
colnames(ersa_seed_set)[2] <- "Treatment"
colnames(ersa_seed_set)[3] <- "Treatment.number"
colnames(ersa_seed_set)[4] <- "Seed.production"
ersa_seed_set <- rbind(ersa_seed_set, ersa_50, ersa_100)
ersa_seed_set$Treatment<- as.character(ersa_seed_set$Treatment)
ersa_seed_set <- ersa_seed_set[order(ersa_seed_set$Treatment),]

library(stringr)
ersa_seed_set_div <- str_split_fixed(as.character(ersa_seed_set$Treatment), " ", 2)
ersa_seed_set_div <- data.frame(ersa_seed_set_div, stringsAsFactors = F)
colnames(ersa_seed_set_div)=c("non_focal","percentage")
ersa_seed_set_bind <- cbind(ersa_seed_set,ersa_seed_set_div)
ersa_seed_set_bind <- filter(ersa_seed_set_bind, percentage!="100%")

#Because I want to give it specifically order I do it separately
#pein_seed_set_common <- filter(ersa_seed_set_bind, non_focal %in% c("CROSS", "SELF","CONTROL","FLOWER"))

ersa_seed_set_cross <- filter(ersa_seed_set_bind, non_focal %in% c("Cross"))
ersa_seed_set_self <- filter(ersa_seed_set_bind, non_focal %in% c("Self"))
ersa_seed_set_control <- filter(ersa_seed_set_bind, non_focal %in% c("Control"))
ersa_seed_set_flower <- filter(ersa_seed_set_bind, non_focal %in% c("FC"))

# I HAVENT BEEN ABLE TO WORK OUT ALL AT THE SAME TIME SO i DO IOT SEPARATELY
ersa_seed_set_bind=ersa_seed_set_bind[ersa_seed_set_bind$non_focal!=c("Cross"),]
ersa_seed_set_bind=ersa_seed_set_bind[ersa_seed_set_bind$non_focal!=c("Self"),]
ersa_seed_set_bind=ersa_seed_set_bind[ersa_seed_set_bind$non_focal!=c("Control"),]
ersa_seed_set_bind=ersa_seed_set_bind[ersa_seed_set_bind$non_focal!=c("FC"),]

ersa_seed_set_final<-rbind(ersa_seed_set_bind,ersa_seed_set_cross, ersa_seed_set_self, ersa_seed_set_control,
                           ersa_seed_set_flower)
#deleting extra columns used for data formating
ersa_seed_set_final=ersa_seed_set_final[,-c(5,6)]
#adding NA'S to the focal species
ersa_seed_set_final[ersa_seed_set_final$Treatment==c("ERSA 50%"),4] <- NA

#changing non_focal species name
ersa_seed_set_final$Treatment=as.character(ersa_seed_set_final$Treatment)
ersa_seed_set_final$Family[ersa_seed_set_final$Treatment=="BROL 50%"] <- "Brassicaceae"
ersa_seed_set_final$Family[ersa_seed_set_final$Treatment=="BRRA 50%"] <- "Brassicaceae"
ersa_seed_set_final$Family[ersa_seed_set_final$Treatment=="SIAL 50%"] <- "Brassicaceae"
ersa_seed_set_final$Family[ersa_seed_set_final$Treatment=="ERSA 50%"] <- "Brassicaceae"
ersa_seed_set_final$Family[ersa_seed_set_final$Treatment=="CAAN 50%"] <- "Solanaceae"
ersa_seed_set_final$Family[ersa_seed_set_final$Treatment=="SOLY 50%"] <- "Solanaceae"
ersa_seed_set_final$Family[ersa_seed_set_final$Treatment=="SOME 50%"] <- "Solanaceae"
ersa_seed_set_final$Family[ersa_seed_set_final$Treatment=="PEIN 50%"] <- "Solanaceae"
ersa_seed_set_final$Family[ersa_seed_set_final$Treatment=="IPPU 50%"] <- "Convolvulaceae"
ersa_seed_set_final$Family[ersa_seed_set_final$Treatment=="IPAQ 50%"] <- "Convolvulaceae"

ersa_seed_set_final$Treatment[ersa_seed_set_final$Treatment=="BROL 50%"] <- "Brassica oleracea"
ersa_seed_set_final$Treatment[ersa_seed_set_final$Treatment=="BRRA 50%"] <- "Brassica rapa"
ersa_seed_set_final$Treatment[ersa_seed_set_final$Treatment=="CAAN 50%"] <- "Capsicum annuum"
ersa_seed_set_final$Treatment[ersa_seed_set_final$Treatment=="ERSA 50%"] <- "Eruca vesicaria" #Eruca sativa seems to be a synonym
ersa_seed_set_final$Treatment[ersa_seed_set_final$Treatment=="IPAQ 50%"] <- "Ipomoea aquatica"
ersa_seed_set_final$Treatment[ersa_seed_set_final$Treatment=="IPPU 50%"] <- "Ipomoea purpurea"
ersa_seed_set_final$Treatment[ersa_seed_set_final$Treatment=="PEIN 50%"] <- "Petunia integrifolia"
ersa_seed_set_final$Treatment[ersa_seed_set_final$Treatment=="SIAL 50%"] <- "Sinapis alba"
ersa_seed_set_final$Treatment[ersa_seed_set_final$Treatment=="SOLY 50%"] <- "Solanum lycopersicum"
ersa_seed_set_final$Treatment[ersa_seed_set_final$Treatment=="SOME 50%"] <- "Solanum melongena"

#Different colour per family
c <- ggplot(ersa_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot()+
  labs(title="Eruca versicaria",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.2) + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
#
##
###
#S. ALBA  
###
##
#

sial_seed_set <- read.csv("Data/sial_seed_set.csv", sep=";")
sial_seed_set <- filter(sial_seed_set, Treatment!="RARA 100%" & Treatment!="RARA 50%"& Treatment!="COSA 50%"& Treatment!="COSA 100%" )

#adding the focal species, first 50%
Species <- rep("SIAL", 10)
Treatment <- rep("SIAL 50%", 10)
Treatment.number <- seq(1:10)
Seed.production <- rep(0, 10)
sial_50 <- data.frame(Species,Treatment, Treatment.number, Seed.production)
#adding the focal species, 100%
Species <- rep("SIAL", 10)
Treatment <- rep("SIAL 100%", 10)
Treatment.number <- seq(1:10)
Seed.production <- rep(0, 10)
sial_100<-  data.frame(Species,Treatment, Treatment.number, Seed.production)
#Order from lower to higher values the average, to plot it nicely
colnames(sial_seed_set)[1] <- "Species"
colnames(sial_seed_set)[2] <- "Treatment"
colnames(sial_seed_set)[3] <- "Treatment.number"
colnames(sial_seed_set)[4] <- "Seed.production"
sial_seed_set <- rbind(sial_seed_set, sial_50, sial_100)
sial_seed_set$Treatment<- as.character(sial_seed_set$Treatment)
sial_seed_set <- sial_seed_set[order(sial_seed_set$Treatment),]

library(stringr)
sial_seed_set_div <- str_split_fixed(as.character(sial_seed_set$Treatment), " ", 2)
sial_seed_set_div <- data.frame(sial_seed_set_div, stringsAsFactors = F)
colnames(sial_seed_set_div)=c("non_focal","percentage")
sial_seed_set_bind <- cbind(sial_seed_set,sial_seed_set_div)
sial_seed_set_bind <- filter(sial_seed_set_bind, percentage!="100%")

#Because I want to give it specifically order I do it separately
#pein_seed_set_common <- filter(sial_seed_set_bind, non_focal %in% c("CROSS", "SELF","CONTROL","FLOWER"))

sial_seed_set_cross <- filter(sial_seed_set_bind, non_focal %in% c("Cross"))
sial_seed_set_self <- filter(sial_seed_set_bind, non_focal %in% c("Self"))
sial_seed_set_control <- filter(sial_seed_set_bind, non_focal %in% c("Control"))
sial_seed_set_flower <- filter(sial_seed_set_bind, non_focal %in% c("FC"))

# I HAVENT BEEN ABLE TO WORK OUT ALL AT THE SAME TIME SO i DO IOT SEPARATELY
sial_seed_set_bind=sial_seed_set_bind[sial_seed_set_bind$non_focal!=c("Cross"),]
sial_seed_set_bind=sial_seed_set_bind[sial_seed_set_bind$non_focal!=c("Self"),]
sial_seed_set_bind=sial_seed_set_bind[sial_seed_set_bind$non_focal!=c("Control"),]
sial_seed_set_bind=sial_seed_set_bind[sial_seed_set_bind$non_focal!=c("FC"),]

sial_seed_set_final<-rbind(sial_seed_set_bind,sial_seed_set_cross, sial_seed_set_self, sial_seed_set_control,
                           sial_seed_set_flower)
#deleting extra columns used for data formating
sial_seed_set_final=sial_seed_set_final[,-c(5,6)]
#adding NA'S to the focal species
sial_seed_set_final[sial_seed_set_final$Treatment==c("SIAL 50%"),4] <- NA

#changing non_focal species name
sial_seed_set_final$Treatment=as.character(sial_seed_set_final$Treatment)
sial_seed_set_final$Family[sial_seed_set_final$Treatment=="BROL 50%"] <- "Brassicaceae"
sial_seed_set_final$Family[sial_seed_set_final$Treatment=="BRRA 50%"] <- "Brassicaceae"
sial_seed_set_final$Family[sial_seed_set_final$Treatment=="SIAL 50%"] <- "Brassicaceae"
sial_seed_set_final$Family[sial_seed_set_final$Treatment=="ERSA 50%"] <- "Brassicaceae"
sial_seed_set_final$Family[sial_seed_set_final$Treatment=="CAAN 50%"] <- "Solanaceae"
sial_seed_set_final$Family[sial_seed_set_final$Treatment=="SOLY 50%"] <- "Solanaceae"
sial_seed_set_final$Family[sial_seed_set_final$Treatment=="SOME 50%"] <- "Solanaceae"
sial_seed_set_final$Family[sial_seed_set_final$Treatment=="PEIN 50%"] <- "Solanaceae"
sial_seed_set_final$Family[sial_seed_set_final$Treatment=="IPPU 50%"] <- "Convolvulaceae"
sial_seed_set_final$Family[sial_seed_set_final$Treatment=="IPAQ 50%"] <- "Convolvulaceae"

sial_seed_set_final$Treatment[sial_seed_set_final$Treatment=="BROL 50%"] <- "Brassica oleracea"
sial_seed_set_final$Treatment[sial_seed_set_final$Treatment=="BRRA 50%"] <- "Brassica rapa"
sial_seed_set_final$Treatment[sial_seed_set_final$Treatment=="CAAN 50%"] <- "Capsicum annuum"
sial_seed_set_final$Treatment[sial_seed_set_final$Treatment=="ERSA 50%"] <- "Eruca vesicaria" #Eruca sativa seems to be a synonym
sial_seed_set_final$Treatment[sial_seed_set_final$Treatment=="IPAQ 50%"] <- "Ipomoea aquatica"
sial_seed_set_final$Treatment[sial_seed_set_final$Treatment=="IPPU 50%"] <- "Ipomoea purpurea"
sial_seed_set_final$Treatment[sial_seed_set_final$Treatment=="PEIN 50%"] <- "Petunia integrifolia"
sial_seed_set_final$Treatment[sial_seed_set_final$Treatment=="SIAL 50%"] <- "Sinapis alba"
sial_seed_set_final$Treatment[sial_seed_set_final$Treatment=="SOLY 50%"] <- "Solanum lycopersicum"
sial_seed_set_final$Treatment[sial_seed_set_final$Treatment=="SOME 50%"] <- "Solanum melongena"

#Different colour per family
d <- ggplot(sial_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot()+
  labs(title="Sinapis alba",x="", y = "", tag= "D")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+ theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.2)+ stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") + theme(legend.position="none")

grobz <- lapply(list(a, b, c, d), ggplotGrob)
grobz.plot <- arrangeGrob( grobs = list(rbind(grobz[[1]], grobz[[3]], size = "last"),
                                        rbind(grobz[[2]], grobz[[4]], size = "last")), ncol = 2,top="Brassicaceae Focal species")

```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=3.8}
#load libraries

library(ggplot2)
library(colorspace)
library(gridExtra)

colours <- rainbow_hcl(4, start = 30, end = 300)
#load data

par(mfrow=c(2,1))
d<-read.csv("Data/Ovules.csv", sep=";")
d<- d[,-c(9,11)]
colnames(d)[1]<-"C. annuum"
colnames(d)[2]<-"S. lycopersicum"
colnames(d)[3]<-"S. melongera"
colnames(d)[4]<-"P. integrifolia"
colnames(d)[5]<-"B. oleracea"
colnames(d)[6]<-"B. rapa"
colnames(d)[7]<-"E. sativa"
colnames(d)[8]<-"S. alba"
colnames(d)[9]<-"I. aquatica"
colnames(d)[10]<-"I. purpurea"

#Reorganise data
d <- stack(d)
#Naming columns
colnames(d)[1]<-"ovules"
colnames(d)[2]<-"species"

family<- c(rep("solanaceae",60),rep("brassicaceae",60),rep("convolvulaceae",30))

d[,"family"] <- family

#subset per family (solanaceae, brassicaceae, convolvulaceae)
solanaceae<-subset(d)[1:60,]
brassicaceae<-subset(d)[61:120,]

# OVULES SOLANACEAE
p <- ggplot(solanaceae, aes(x = reorder(species, ovules, FUN = median), y = ovules)) +   geom_boxplot()+
labs(title="Solanaceae",x="", y = "Ovules")+aes(fill=species)+scale_fill_manual(values=colours)+
theme(plot.title = element_text(hjust = 0.5))

p + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")

# OVULES BRASSICACEAE
p <- ggplot(brassicaceae, aes(x = reorder(species, ovules, FUN = median), y = ovules)) +   geom_boxplot()+
labs(title="Brassicaceae",x="", y = "Ovules")+aes(fill=species)+scale_fill_manual(values=colours)+
theme(plot.title = element_text(hjust = 0.5))

p + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")

#all species
#formating d, to have just the spp of interest

p <- ggplot(d, aes(x = reorder(species, ovules, FUN = median), y = ovules)) +   geom_boxplot()+
labs(title="Ovules per spp.",x="", y = "Ovules")+aes(fill=family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
theme(plot.title = element_text(hjust = 0.5))

p + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")

#Pollen per anther, just one Convolvulaceae at the moment
```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=3}
library(ggplot2)

p <- read.csv("data/Pollen.csv", sep = ";")

#Deleting extra row (21)
p <-p[-21,]

#boxplot(p)
#Reorganize data for ggplot
p<-stack(p)
#colnames
colnames(p)[1]<-"pollen"
colnames(p)[2]<-"species"

all<-p
solanaceae<-subset(p)[1:100,]
brassicaceae<- subset(p)[101:180,]

#Solanaceae
p <- ggplot(solanaceae, aes(x = reorder(species, pollen, FUN = median), y = pollen)) +   geom_boxplot()+
labs(title="Solanaceae",x="", y = "pollen")+aes(fill=species)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
theme(plot.title = element_text(hjust = 0.5))

p + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")

#Brassicaceae
p <- ggplot(brassicaceae, aes(x = reorder(species, pollen, FUN = median), y = pollen)) +   geom_boxplot()+
labs(title="Brassicaceae",x="", y = "pollen")+aes(fill=species)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
theme(plot.title = element_text(hjust = 0.5))

p + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")

#all
p <- ggplot(all, aes(x = reorder(species, pollen, FUN = median), y = pollen)) +   geom_boxplot()+
labs(title="All species",x="", y = "pollen")+aes(fill=species)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
theme(plot.title = element_text(hjust = 0.5))

p + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
```

```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=6}
tab <- read.csv("Data/tab.csv", sep="", header = T)

p <- ggplot(data=tab, aes(x=reorder(species, pollen_ovule_ratio, colour = cut), y=pollen_ovule_ratio))+aes(fill=family)+
  geom_bar(stat="identity", width=0.5)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
  scale_fill_manual(values=colours)
p + ggtitle("Pollen/ovule ratio per species") + theme(plot.title = element_text(hjust = 0.5))+ labs(x = "Species")

```{r echo=FALSE, out.width='80%', fig.align='center'}
knitr::include_graphics('Images/all_species.png')
```

\newpage
```{r,echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=6, fig.width=8,out.width='100%'}
par(mfrow=c(2,2))
#load libraries
library(reshape2)
library(ggplot2)
#read data
pein_seed_set <- read.csv("Data/PEIN_seed_set.csv", sep=";")
pein_seed_set <- pein_seed_set[-c(42,47,49),]

mean_seed_seet <- dcast(Treatment ~ ., value.var = "Seed.production", fun.aggregate = mean, data = pein_seed_set, na.rm= TRUE)

colnames(mean_seed_seet)[2] <-"avg"

sd_seed_seet <- dcast(Treatment ~ ., value.var = "Seed.production", fun.aggregate = sd, data = pein_seed_set, na.rm= TRUE)

colnames(sd_seed_seet)[2] <-"sdev"

#Unify mean and sd with merge
mean_sd <- merge(mean_seed_seet,sd_seed_seet, by="Treatment")
#Removing RARA, species not considered because sterility 
mean_sd<- mean_sd[-c(16,17),]

merge_1 <- data.frame(mean_sd, stringsAsFactors = F)

merge_1$Treatment<- as.character(merge_1$Treatment)
pein <- c("PEIN", NA, NA)

str(merge_1)
mean_sd_1 <- rbind(merge_1,pein)

#Order from lower to higher values the average, to plot it nicely
mean_sd_ordered <- mean_sd[order(mean_sd$avg),]

mean_sd_ordered_alphabetically<- mean_sd_ordered[order(mean_sd_ordered$Treatment),]

#ploting averages with sd
x <- 1:22
plot(x, mean_sd_ordered$avg,
     ylim=range(c(mean_sd_ordered$avg-mean_sd_ordered$sdev, mean_sd_ordered$avg+mean_sd_ordered$sdev)),
     pch=19, xlab="", xaxt='n', ylab="Mean +/- SD",
     main="Petunia integrifolia")
# add arrows
arrows(x, mean_sd_ordered$avg-mean_sd_ordered$sdev, x, mean_sd_ordered$avg+mean_sd_ordered$sdev, length=0.05, angle=90, code=3)
lablist.x<-as.vector(mean_sd_ordered$Treatment)
axis(x, at=1:22, labels = FALSE)
text(x, par("usr")[3] - 0.2, labels = lablist.x, cex= 0.6, adj = 1.25,srt = 45, xpd = TRUE)

>>>>

---
title: ''
output:
  pdf_document: default
  html_document: default
---
```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=6, fig.width=7,out.width='100%'}
#Preparing seed set plots, starting with Petunia

@@

grobz <- lapply(list(a, b, c, d), ggplotGrob)
grobz.plot <- arrangeGrob( grobs = list(rbind(grobz[[1]], grobz[[3]], size = "last"),
                                        rbind(grobz[[2]], grobz[[4]], size = "last")),
                           ncol = 2, top="b")

@@
